---
title: "Matt Chana"
output: html_document
---
***  
##### Contact:

email: `matthewchana@gmail.com`

***
##### Profiles:

[Udacity](https://profiles.udacity.com/p/6660788570)

[LinkedIn](https://www.linkedin.com/in/matthewchana)

[Github](https://github.com/rancherobeans)

***
##### Projects:
[OpenStreetMap - A Data Cleaning Case Study](https://github.com/rancherobeans/udacity/blob/master/P3/PROJECT/OpenStreetMap_CaseStudy.ipynb):

* A guide to cleaning and drawing insights from OpenStreetMap data of the New Orleans watershed
* Parsed XML data with Python scripting and gathered insights using SQL queries


[Stroop Effect Investigation](https://github.com/rancherobeans/udacity/blob/master/P1/P1-Stroop-Effect-Investigation.ipynb):

* A novel exploration of MLB statistics comparing measures of success with field position adaptability
* Formulated an inferential statistical model with visualizations using Pandas, Numpy and Seaborn


[Lahman Baseball Database Investigation](https://github.com/rancherobeans/udacity/blob/master/P2/project/P2-Lahman-Baseball-Database-Investigation.ipynb): 

* A statistical investigation into the classical Stroop Effect Test experiment in psychology
* Constructed a dependent t-test for paired samples hypothesis test using Python’s Scipy framework

***
##### Plot:
```{r include = FALSE}
library(viridis)
library(jpeg)
```

```{r}
# load Matt
img <- readJPEG("matt.jpg")

# flip Matt
rv <- rev(img)

# reshape Matt for heatmap aspect ratio
m <- matrix(rv, nrow = 582, ncol = 363, byrow = TRUE)

# make Matt into heatmap
image(z = m, main="Matt", col = viridis(200, option = "A"))
```


<script>
  (function(i,s,o,g,r,a,m){i['GoogleAnalyticsObject']=r;i[r]=i[r]||function(){
  (i[r].q=i[r].q||[]).push(arguments)},i[r].l=1*new Date();a=s.createElement(o),
  m=s.getElementsByTagName(o)[0];a.async=1;a.src=g;m.parentNode.insertBefore(a,m)
  })(window,document,'script','https://www.google-analytics.com/analytics.js','ga');

  ga('create', 'UA-11851098-7', 'auto');
  ga('send', 'pageview');

</script>